### 2020-01-22 article_draft.tex
Updates from Overleaf

It follows that if $\mu_n \rightarrow \mu$, and $\Sigma_n \rightarrow \Sigma$, then for each $x$, $\psi(x, \mu_n, \Sigma_n) \rightarrow \psi(x, \mu, \Sigma)$.
This result and the dominated convergence theorem imply the corresponding CDF's are also continuous ($\phi(x, \hat{\mu}, \hat{\Sigma}) + \phi(x, \mu, \Sigma)$ can be used as the dominating measure):

@@

@@

\begin{align*}
	\Gamma_{\hat{\Sigma}}(x) - \Gamma_{\Sigma}(x) &= Pr_{\hat{\distv}}(||\rvv^* + x|| > \Phi^{-1}_{\hat{\Sigma}, 0}(0.8)) - Pr_{\distv}(||\rvv^* + x|| > \Phi^{-1}_{\Sigma, 0}(0.8))\\
	&\leq \int_{\mathbb{R}^d} |\phi(t, x, \hat{\Sigma}) I\{||t|| > \Phi^{-1}_{\hat{\Sigma}, 0}(0.8) \} - \phi(t, x, \Sigma) I\{||t|| > \Phi^{-1}_{\Sigma, 0}(0.8) \}|dt \\ 
	& = \int_{||t|| > \Phi^{-1}_{\hat{\Sigma}, 0}(0.8), \Phi^{-1}_{\Sigma, 0}(0.8)} |\phi(t, x, \hat{\Sigma}) - \phi(t, x, \Sigma)|dt + \\
	& \hspace{5em} \int_{\Phi^{-1}_{\Sigma, 0}(0.8) \geq ||t|| > \Phi^{-1}_{\hat{\Sigma}, 0}(0.8)} |\phi(t, x, \hat{\Sigma})|dt + \int_{\Phi^{-1}_{\hat{\Sigma}, 0}(0.8) \geq ||t|| > \Phi^{-1}_{\Sigma, 0}(0.8)} | \phi(t, x, \Sigma)|dt \\
	& \leq \int_{||t|| > \Phi^{-1}_{\Sigma, 0}(0.8)} |\phi(t, x, \hat{\Sigma}) - \phi(t, x, \Sigma)|dt + \\
	& \hspace{5em} \int_{\Phi^{-1}_{\Sigma, 0}(0.8) \geq ||t|| > \Phi^{-1}_{\hat{\Sigma}, 0}(0.8)} \phi(t, x, \hat{\Sigma})dt + \int_{\Phi^{-1}_{\hat{\Sigma}, 0}(0.8) \geq ||t|| > \Phi^{-1}_{\Sigma, 0}(0.8)} \phi(t, x, \Sigma)dt \\
	& = \int_{||t|| > \Phi^{-1}_{\Sigma, 0}(0.8)} |\phi(t, x, \hat{\Sigma}) - \phi(t, x, \Sigma)|dt + \\
	& \hspace{5em} \Phi_{\hat{\Sigma}, x}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\hat{\Sigma}, x}(\Phi^{-1}_{\hat{\Sigma}, 0}(0.8)) + \Phi_{\Sigma, x}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\Sigma, x}(\Phi^{-1}_{\hat{\Sigma}, 0}(0.8)) \\
	& = \int_{||t|| > \Phi^{-1}_{\Sigma, 0}(0.8)} |\phi(t, x, \hat{\Sigma}) - \phi(t, x, \Sigma)|dt + \\
	& \hspace{5em} \Phi_{\hat{\Sigma}, x}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\hat{\Sigma}, x}(\Phi^{-1}_{\hat{\Sigma}, 0}(0.8)) - \left(\Phi_{\Sigma, x}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\Sigma, x}(\Phi^{-1}_{\hat{\Sigma}, 0}(0.8))\right)+\\
	& \hspace{5em} \left(\Phi_{\Sigma, x}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\Sigma, x}(\Phi^{-1}_{\hat{\Sigma}, 0}(0.8))\right) +  \Phi_{\Sigma, x}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\Sigma, x}(\Phi^{-1}_{\hat{\Sigma}, 0}(0.8)) \\
	& = \int_{||t|| > \Phi^{-1}_{\Sigma, 0}(0.8)} |\phi(t, x, \hat{\Sigma}) - \phi(t, x, \Sigma)|dt + \\
	& \hspace{5em} \left(\Phi_{\hat{\Sigma}, x}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\Sigma, x}(\Phi^{-1}_{\Sigma, 0}(0.8)) \right) - \left(\Phi_{\hat{\Sigma}, x}(\Phi^{-1}_{\hat{\Sigma}, 0}(0.8)) -  \Phi_{\Sigma, x}(\Phi^{-1}_{\hat{\Sigma}, 0}(0.8))\right)+\\
	& \hspace{5em} \left(\Phi_{\Sigma, x}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\Sigma, x}(\Phi^{-1}_{\hat{\Sigma}, 0}(0.8))\right) +  \Phi_{\Sigma, x}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\Sigma, x}(\Phi^{-1}_{\hat{\Sigma}, 0}(0.8)) \\
\end{align*}

@@

To prove unbiasedness at local alternatives, we show 
\begin{align*}
	F_{\Sigma, t}(F^{-1}_{\Sigma, 0}(1 - \alpha)) \geq F_{\Sigma, 0}(F^{-1}_{\Sigma, 0}(1 - \alpha)) = \alpha
\end{align*}
using results from the \citep{anderson_integral_1955} manuscript.
% \textcolor{blue}{What is $\rvv^* \overset{d}{=} \rvv$ telling us? Don't we already know that the probabilities over both of these quantities are indexed by $Q$? Also, why use different notation at all? Why not just $\rvv^*$ for both? Here because $c_{0.8}$ is not random so this is distinction does not need to be made.}
% In this scenario, the test can be carried out by comparing our test statistic, $\Gamma_\vmat(\sqrt{n}\hat{\boldsymbol{\psi}}, ||\cdot||)$ to $\Gamma_\vmat(\rvv, ||\cdot||).$

A result of \citep{anderson_integral_1955} is that for two centrally symmetric, unimodal functions, $f_1(x)$ and  $f_2(x)$, the convolution,  
\begin{align*}
	g(\theta) = \int f_1(x) f_2(x - \theta)
\end{align*}
is centrally symmetric and ray decreasing.  A function $f(x)$ on $\mathbb{R}^p$ is centrally symmetric if $f(-x) = f(x)$ for every $x$.  A function is unimodal if for every $k$, the set $\{x : f(x) \geq k\}$ is convex. A function $f(x)$ on $\mathbb{R}^p$ is ray decreasing if for every $x$ in $\mathbb{R}^p$, the function $g(\beta) = f(\beta x), \beta \in \mathbb{R}$ is a decreasing function of $\beta$.

>>>>

It follows that if $\mu_n \rightarrow \mu$, and $\Sigma_n \rightarrow \Sigma$, then for each $x$, $\phi(x, \mu_n, \Sigma_n) \rightarrow \phi(x, \mu, \Sigma)$.
This result and the dominated convergence theorem imply the corresponding CDF's are also continuous ($\phi(x, \hat{\mu}, \hat{\Sigma}) + \phi(x, \mu, \Sigma)$ can be used as the dominating measure): \textcolor{blue}{(dominating function shouldn't depend on $n$)}

@@

\textcolor{blue}{Show (or find reference showing that) $\Phi_{\Sigma_n,0}^{-1}(0.8)\rightarrow \Phi_{\Sigma,0}^{-1}(0.8)$ when $\Sigma_n\rightarrow \Sigma$. E.g., implicit function theorem will do this}

@@

\begin{align*}
	\left|\Gamma_{\hat{\Sigma}}(x) - \Gamma_{\Sigma}(x)\right| &= \left|Pr_{\hat{\distv}}(||\rvv^* + x|| > \Phi^{-1}_{\hat{\Sigma}, 0}(0.8)) - Pr_{\distv}(||\rvv^* + x|| > \Phi^{-1}_{\Sigma, 0}(0.8))\right|\\
	&= \left|\int_{\mathbb{R}^d} \phi(t, 0, \hat{\Sigma}) I\{||t+x|| > \Phi^{-1}_{\hat{\Sigma}, 0}(0.8) \} - \phi(t, 0, \Sigma) I\{||t+x|| > \Phi^{-1}_{\Sigma, 0}(0.8) \}dt \right| \\ 
	&= \left|\int_{\mathbb{R}^d} \phi(t, x, \hat{\Sigma}) I\{||t|| > \Phi^{-1}_{\hat{\Sigma}, 0}(0.8) \} - \phi(t, x, \Sigma) I\{||t|| > \Phi^{-1}_{\Sigma, 0}(0.8) \}dt \right| \\ 
	&\leq \int_{\mathbb{R}^d} |\phi(t, x, \hat{\Sigma}) I\{||t|| > \Phi^{-1}_{\hat{\Sigma}, 0}(0.8) \} - \phi(t, x, \Sigma) I\{||t|| > \Phi^{-1}_{\Sigma, 0}(0.8) \}|dt \\ 
	& = \int_{||t|| > \Phi^{-1}_{\hat{\Sigma}, 0}(0.8), \Phi^{-1}_{\Sigma, 0}(0.8)} |\phi(t, x, \hat{\Sigma}) - \phi(t, x, \Sigma)|dt + \\
	& \hspace{5em} \int_{\Phi^{-1}_{\Sigma, 0}(0.8) \geq ||t|| > \Phi^{-1}_{\hat{\Sigma}, 0}(0.8)} |\phi(t, x, \hat{\Sigma})|dt + \int_{\Phi^{-1}_{\hat{\Sigma}, 0}(0.8) \geq ||t|| > \Phi^{-1}_{\Sigma, 0}(0.8)} | \phi(t, x, \Sigma)|dt \\
	& \leq \int_{||t|| > \Phi^{-1}_{\Sigma, 0}(0.8)} |\phi(t, x, \hat{\Sigma}) - \phi(t, x, \Sigma)|dt + \\
	& \hspace{5em} \int_{\Phi^{-1}_{\Sigma, 0}(0.8) \geq ||t|| > \Phi^{-1}_{\hat{\Sigma}, 0}(0.8)} \phi(t, x, \hat{\Sigma})dt + \int_{\Phi^{-1}_{\hat{\Sigma}, 0}(0.8) \geq ||t|| > \Phi^{-1}_{\Sigma, 0}(0.8)} \phi(t, x, \Sigma)dt \\
	& = \int_{||t|| > \Phi^{-1}_{\Sigma, 0}(0.8)} |\phi(t, x, \hat{\Sigma}) - \phi(t, x, \Sigma)|dt + \\
	& \hspace{5em} \Phi_{\hat{\Sigma}, x}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\hat{\Sigma}, x}(\Phi^{-1}_{\hat{\Sigma}, 0}(0.8)) + \Phi_{\Sigma, x}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\Sigma, x}(\Phi^{-1}_{\hat{\Sigma}, 0}(0.8)) \\
	& = \int_{||t|| > \Phi^{-1}_{\Sigma, 0}(0.8)} |\phi(t, x, \hat{\Sigma}) - \phi(t, x, \Sigma)|dt + \\
	& \hspace{5em} \Phi_{\hat{\Sigma}, x}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\hat{\Sigma}, x}(\Phi^{-1}_{\hat{\Sigma}, 0}(0.8)) - \left(\Phi_{\Sigma, x}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\Sigma, x}(\Phi^{-1}_{\hat{\Sigma}, 0}(0.8))\right)+\\
	& \hspace{5em} \left(\Phi_{\Sigma, x}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\Sigma, x}(\Phi^{-1}_{\hat{\Sigma}, 0}(0.8))\right) +  \Phi_{\Sigma, x}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\Sigma, x}(\Phi^{-1}_{\hat{\Sigma}, 0}(0.8)) \\
	& = \int_{||t|| > \Phi^{-1}_{\Sigma, 0}(0.8)} |\phi(t, x, \hat{\Sigma}) - \phi(t, x, \Sigma)|dt + \\
	& \hspace{5em} \left(\Phi_{\hat{\Sigma}, x}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\Sigma, x}(\Phi^{-1}_{\Sigma, 0}(0.8)) \right) - \left(\Phi_{\hat{\Sigma}, x}(\Phi^{-1}_{\hat{\Sigma}, 0}(0.8)) -  \Phi_{\Sigma, x}(\Phi^{-1}_{\hat{\Sigma}, 0}(0.8))\right)+\\
	& \hspace{5em} \left(\Phi_{\Sigma, x}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\Sigma, x}(\Phi^{-1}_{\hat{\Sigma}, 0}(0.8))\right) +  \Phi_{\Sigma, x}(\Phi^{-1}_{\Sigma, 0}(0.8)) - \Phi_{\Sigma, x}(\Phi^{-1}_{\hat{\Sigma}, 0}(0.8)) \\
\end{align*}
\textcolor{blue}{LHS should be $|\Gamma_{\Sigma_n}(x_n) - \Gamma_{\Sigma}(x)|$}

@@

To prove unbiasedness at local alternatives, we show \textcolor{blue}{$>$?}
\begin{align*}
	F_{\Sigma, t}(F^{-1}_{\Sigma, 0}(1 - \alpha)) \geq F_{\Sigma, 0}(F^{-1}_{\Sigma, 0}(1 - \alpha)) = \alpha
\end{align*}
using results from the \citep{anderson_integral_1955} manuscript.
% \textcolor{blue}{What is $\rvv^* \overset{d}{=} \rvv$ telling us? Don't we already know that the probabilities over both of these quantities are indexed by $Q$? Also, why use different notation at all? Why not just $\rvv^*$ for both? Here because $c_{0.8}$ is not random so this is distinction does not need to be made.}
% In this scenario, the test can be carried out by comparing our test statistic, $\Gamma_\vmat(\sqrt{n}\hat{\boldsymbol{\psi}}, ||\cdot||)$ to $\Gamma_\vmat(\rvv, ||\cdot||).$

A result of \citep{anderson_integral_1955} is that for two centrally symmetric, unimodal functions, $f_1(x)$ and  $f_2(x)$, the convolution,  
\begin{align*}
	g(\theta) = \int f_1(x) f_2(x - \theta)
\end{align*}
is centrally symmetric and ray decreasing.  A function $f :\mathbb{R}^p\rightarrow\mathbb{R}$ is centrally symmetric if $f(-x) = f(x)$ for every $x$.  A function is unimodal if for every $k$, the set $\{x : f(x) \geq k\}$ is convex. A function $f$ on $\mathbb{R}^p$ is ray decreasing if for every $x$ in $\mathbb{R}^p$, the function $g(\beta) = f(\beta x), \beta \in \mathbb{R}$ is a decreasing function of $\beta$.
